\section{Workflows for Model Parameter Validation}

\subsection{Cherenkov photon density}

Cherenkov photon densities vs distance to shower core for different primary energies

\subsection{Effective area calculator}

Calculate effective areas for a given set of model parameters. Comparison to a reference set of simulations.

\subsection{Atmospheric transmission comparison}

Compare transmission probabilities as function of wavelengths for different emission heights.

\subsection{Muon simulation and calibration (optical throughput and optical PSF)}

Simulation muons and run muon calibrator. Compare intensity distribution, camera pixel-wise intensity, optical PSF.

\subsection{Precision optical simulation}

Compare optical throughput between production simulation software and precision of optical simulations.
Comparison should be performed at least as function of distance to the centre of the FOV.


\subsection{Optical efficiency from external light source}

Simulation of external light source (illuminator), analysis, and calculation of optical throughput

\subsection{Brightness of equidistant showers}

Compare image brightness of simulated gamma-ray showers equidistant events seen by pairs of telescopes with a similar selection from data.
\TODO{Simulate gamma rays or hadronic showers?}

\subsection{Telescope trigger rates}

Comparison of telescope trigger rates between simulated events and data.

\subsection{Gamma-ray point-spread function}

Compare gamma-ray point-spread function with measurements obtained from the observation of strong gamma-ray sources.
Take dependency on energy, offset in FOV, elevation, etc., into account.

\subsection{Image parameter comparison}

Compare image parameters obtained from simulated events with data:
\begin{itemize}
    \item excess gamma-ray like events from observations of strong gamma-ray sources with simulated gamma-ray events
    \item hadronic events from 'empty field' observations with simulated hadronic events
\end{itemize}

\subsection{Relative cut efficiencies}

Compare relative cut efficiencies between simulated events with a given simulation model and 
\begin{itemize}
    \item reference simulation production
    \item events from strong gamma-ray emitters
\end{itemize}

\subsection{Trigger probabilities as function of telescopes}

Comparison of trigger probabilities of a third telescope compared to a given telescope pair as a function of distance for simulated hadronic events with data.

\subsection{Validation under non-standard conditions}

Execute validation workflows for observations under non-standard conditions (e.g., high aerosol intrusion, partical cloud coverage)